Human Factors Influencing Visual Statistical Inference

### 2015-08-31 sociology_paper.Rnw
done for now, I think
added two references and comparison to surveys

\subsection{Demographic Factors}  %In addition to obtain evaluation responses of the lineups, all the 10 experiments shown in Table~\ref{tbl:visual_stat} were designed to collect the following demographic information of the subjects participating the experiments:
\hh{XXX compare demographics to US Census data - we see relatively young, relatively highly educated participants compared to general population. Being amazon turkers implicitly assures a relatively high level of technological fluency. }
\noindent
For all  ten experiments shown in Table~\ref{tbl:visual_stat}, the following demographic information was collected from subjects:

@@

@@

% latex table generated in R 3.2.2 by xtable 1.7-4 package
% Sat Aug 29 14:17:22 2015
\begin{table}[hbtp]
\caption{\label{tbl:model_result_demographics}Parameter estimates of models~\eqref{eqn:demographic_time} and~\eqref{eqn:demographic_response} fitted for average log time taken and detection rate, respectively. For time taken all the demographic factors are significant. For detection rate, age group 36-40, rest of the world and graduate degree are significantly different. For gender no difference in performance is observed. Lineup variability is estimated to be very large for model~\eqref{eqn:demographic_response}.}
\centering
\scalebox{.85}{
\begin{tabular}{rrr>{( }r<{,}>{\hspace{-.1in}}l<{)}>{\hspace{-.15in}}l<{}cr>{( }r<{,}>{\hspace{-.1in}}l<{)}>{\hspace{-.15in}}l<{}}
 && \multicolumn{4}{c} {Log Time (model~\ref{eqn:demographic_time})} & &\multicolumn{4}{c} {Detection rate (model~\ref{eqn:demographic_response})}  \\

@@

% latex table generated in R 3.2.2 by xtable 1.7-4 package
% Sun Aug 30 11:15:41 2015
\begin{table}[hbtp]
\centering
\caption{\label{tbl:model_result_response}Parameter estimates of models \eqref{eqn:trend_response} fitted to data from three different experiments using detection rate as the response to assess learning trend. Attempt number is fitted as a factor to enable modeling any sort of non-linear learning trend. Only experiment~6 shows some evidence of a learning trend, with detection rate essentially increasing as attempts increase.}
\scalebox{.81}{
\begin{tabular}{rr>{( }r<{,}>{\hspace{-.1in}}l<{)}>{\hspace{-.15in}}l<{}cr>{( }r<{,}>{\hspace{-.1in}}l<{)}>{\hspace{-.15in}}l<{}cr>{( }r<{,}>{\hspace{-.1in}}l<{)}>{\hspace{-.15in}}l<{}}
\cline{2-5} \cline{7-10} \cline{12-15} 
& \multicolumn{4}{c} {Experiment~5} & &\multicolumn{4}{c} {Experiment~6} && \multicolumn{4}{c} {Experiment~7}\\
\cline{2-5} \cline{7-10} \cline{12-15} 
Effect & Est & 2.5\% & 97.5\% &  & \hspace{1cm} & Est & 2.5\% & 97.5\% &  & \hspace{1cm} & Est & 2.5\% & 97.5\% &  \\ 
\cline{2-5} \cline{7-10} \cline{12-15} 
Fixed \\
$\mu$ & -1.30 & -1.69 & -0.92 & *** &   & -0.22 & -0.51 & 0.07 &  &   & -1.71 & -2.77 & -0.65 & ** \\ [3pt]
  $\alpha_2$ & 0.27 & -0.19 & 0.73 &  &   & 0.26 & -0.06 & 0.58 &  &   & -0.49 & -1.31 & 0.32 &  \\ 
  $\alpha_3$ & -0.18 & -0.65 & 0.29 &  &   & 0.34 & 0.02 & 0.66 & * &   & -0.19 & -1.01 & 0.63 &  \\ 
  $\alpha_4$ & 0.08 & -0.39 & 0.55 &  &   & 0.36 & 0.04 & 0.68 & * &   & -0.47 & -1.28 & 0.35 &  \\ 
  $\alpha_5$ & 0.30 & -0.17 & 0.77 &  &   & 0.37 & 0.05 & 0.70 & * &   & -0.16 & -0.96 & 0.65 &  \\ 
  $\alpha_6$ & 0.04 & -0.44 & 0.53 &  &   & 0.24 & -0.07 & 0.56 &  &   & -0.03 & -0.87 & 0.82 &  \\ 
  $\alpha_7$ & 0.28 & -0.20 & 0.77 &  &   & 0.16 & -0.16 & 0.48 &  &   & 0.02 & -0.81 & 0.84 &  \\ 
  $\alpha_8$ & -0.04 & -0.54 & 0.45 &  &   & 0.34 & 0.02 & 0.66 & * &   & -0.08 & -0.89 & 0.73 &  \\ 
  $\alpha_9$ & -0.20 & -0.69 & 0.30 &  &   & 0.38 & 0.05 & 0.70 & * &   & 0.15 & -0.71 & 1.02 &  \\ 
  $\alpha_{10}$ & 0.51 & 0.03 & 1.00 & * &   & 0.19 & -0.14 & 0.52 &  &   & -0.28 & -1.14 & 0.58 &  \\ 
  Random \\
  $\sigma^2_u$ & \multicolumn{5}{l}{\phantom{-}0.85}  & \multicolumn{5}{l}{\phantom{-}0.90} & 0.76   \\ 
  $\sigma^2_a$ & \multicolumn{5}{l}{\phantom{-}0.02}  & \multicolumn{5}{l}{\phantom{-}0.03} & 0.06   \\ 
  $\sigma^2_l$ & \multicolumn{5}{l}{\phantom{-}1.48}  & \multicolumn{5}{l}{\phantom{-}1.42} & 3.37   \\ \cline{2-5} \cline{7-10} \cline{12-15} 
\\
\hline
\multicolumn{10}{l}{Signif. codes:  *** $<$ 0.001 $\le$ ** $<$ 0.01 $\le$ * $<$ 0.05 $\le$ . $<$ 0.1 $\le$ ` ' $<$ 1}
\end{tabular}}
\end{table}

>>>>

\subsection{Demographic Factors}  %In addition to obtain evaluation responses of the lineups, all the 10 experiments shown in Table~\ref{tbl:visual_stat} were designed to collect the following demographic information of the subjects participating the experiments:
\noindent
For all  ten experiments shown in Table~\ref{tbl:visual_stat}, the following demographic information was collected from subjects:

@@

Compared to data from the 2010 US Census \cite{census}, participants were both relatively younger, and more highly educated than the general US population. 
Being turkers implicitly assures that the participants in these experiments have a relatively high level of technological fluency. In fact, the demographics of participants align somewhat better with demographics of internet users published by
\citet{pew}.

@@

% latex table generated in R 3.2.2 by xtable 1.7-4 package
% Sat Aug 29 14:17:22 2015
\begin{table}[hbtp]
\caption{\label{tbl:model_result_demographics}Parameter estimates of models~\eqref{eqn:demographic_time} and~\eqref{eqn:demographic_response} fitted for average log time taken and detection rate, respectively. For time taken all the demographic factors are significant. For detection rate, age group 36-40, rest of the world and graduate degree are significantly different. For gender no difference in performance is observed. Lineup variability is estimated to be very large for model~\eqref{eqn:demographic_response}.}
\centering
\scalebox{.9}{
\begin{tabular}{rrr>{( }r<{,}>{\hspace{-.1in}}l<{)}>{\hspace{-.15in}}l<{}cr>{( }r<{,}>{\hspace{-.1in}}l<{)}>{\hspace{-.15in}}l<{}}
 && \multicolumn{4}{c} {Log Time (model~\ref{eqn:demographic_time})} & &\multicolumn{4}{c} {Detection rate (model~\ref{eqn:demographic_response})}  \\

@@

% latex table generated in R 3.2.2 by xtable 1.7-4 package
% Sun Aug 30 11:15:41 2015
\begin{table}[hbtp]
\centering
\caption{\label{tbl:model_result_response}Parameter estimates of models \eqref{eqn:trend_response} fitted to data from three different experiments using detection rate as the response to assess learning trend. Attempt number is fitted as a factor to enable modeling any sort of non-linear learning trend. Only experiment~6 shows some evidence of a learning trend, with detection rate essentially increasing as attempts increase.}
\scalebox{.9}{
\begin{tabular}{rr>{( }r<{,}>{\hspace{-.1in}}l<{)}>{\hspace{-.15in}}l<{}cr>{( }r<{,}>{\hspace{-.1in}}l<{)}>{\hspace{-.15in}}l<{}cr>{( }r<{,}>{\hspace{-.1in}}l<{)}>{\hspace{-.15in}}l<{}}
\cline{2-5} \cline{7-10} \cline{12-15} 
& \multicolumn{4}{c} {Experiment~5} & &\multicolumn{4}{c} {Experiment~6} && \multicolumn{4}{c} {Experiment~7}\\
\cline{2-5} \cline{7-10} \cline{12-15} 
Effect & Est & 2.5\% & 97.5\% &  & \hspace{1cm} & Est & 2.5\% & 97.5\% &  & \hspace{1cm} & Est & 2.5\% & 97.5\% &  \\ 
\cline{2-5} \cline{7-10} \cline{12-15} 
Fixed \\
$\mu$ & -1.30 & -1.69 & -0.92 & *** &   & -0.22 & -0.51 & 0.07 &  &   & -1.71 & -2.77 & -0.65 & ** \\ [3pt]
  $\alpha_2$ & 0.27 & -0.19 & 0.73 &  &   & 0.26 & -0.06 & 0.58 &  &   & -0.49 & -1.31 & 0.32 &  \\ 
  $\alpha_3$ & -0.18 & -0.65 & 0.29 &  &   & 0.34 & 0.02 & 0.66 & * &   & -0.19 & -1.01 & 0.63 &  \\ 
  $\alpha_4$ & 0.08 & -0.39 & 0.55 &  &   & 0.36 & 0.04 & 0.68 & * &   & -0.47 & -1.28 & 0.35 &  \\ 
  $\alpha_5$ & 0.30 & -0.17 & 0.77 &  &   & 0.37 & 0.05 & 0.70 & * &   & -0.16 & -0.96 & 0.65 &  \\ 
  $\alpha_6$ & 0.04 & -0.44 & 0.53 &  &   & 0.24 & -0.07 & 0.56 &  &   & -0.03 & -0.87 & 0.82 &  \\ 
  $\alpha_7$ & 0.28 & -0.20 & 0.77 &  &   & 0.16 & -0.16 & 0.48 &  &   & 0.02 & -0.81 & 0.84 &  \\ 
  $\alpha_8$ & -0.04 & -0.54 & 0.45 &  &   & 0.34 & 0.02 & 0.66 & * &   & -0.08 & -0.89 & 0.73 &  \\ 
  $\alpha_9$ & -0.20 & -0.69 & 0.30 &  &   & 0.38 & 0.05 & 0.70 & * &   & 0.15 & -0.71 & 1.02 &  \\ 
  $\alpha_{10}$ & 0.51 & 0.03 & 1.00 & * &   & 0.19 & -0.14 & 0.52 &  &   & -0.28 & -1.14 & 0.58 &  \\ 
  Random \\
  $\sigma^2_u$ & \multicolumn{5}{l}{\phantom{-}0.85}  & \multicolumn{5}{l}{\phantom{-}0.90} & 0.76   \\ 
  $\sigma^2_a$ & \multicolumn{5}{l}{\phantom{-}0.02}  & \multicolumn{5}{l}{\phantom{-}0.03} & 0.06   \\ 
  $\sigma^2_l$ & \multicolumn{5}{l}{\phantom{-}1.48}  & \multicolumn{5}{l}{\phantom{-}1.42} & 3.37   \\ \cline{2-5} \cline{7-10} \cline{12-15} 
\\
\hline
\multicolumn{10}{l}{Signif. codes:  *** $<$ 0.001 $\le$ ** $<$ 0.01 $\le$ * $<$ 0.05 $\le$ . $<$ 0.1 $\le$ ` ' $<$ 1}
\end{tabular}}
\end{table}
